\MakeUppercase{Layered Partitions of $k$-Planar Graphs} \thanks{This work was partly funded by NSERC and MRI.}

### 2019-05-23 k-planar.tex
Some rewording

\begin{lem}
  Every $(g,\delta)$-string graph $G$ is a $(g,\delta^2)$-planar graph.
\end{lem}

\begin{proof}
  Consider some $(S,\delta)$-string representation, $f$, of $G$.  We will describe an embedding of $G$ into $S$ that is an $(S,k)$-plane graph.  Each vertex $v\in v(G)$ is embedded at $f(v)(0)$. For each edge $vw\in E(G)$ there is an intersection point $p$ between $f(v)$ and $f(w)$, i.e., $f(v)(t_0)=f(w)(t_1)=p$ for some $t_0,t_1\in[0,1]$.  Embed the edge $vw$ very close to the curve whose image is $\{f(v)(t): 0\le t\le t_1\}\cup f(w)(t): 0 \le t\le t_2\}$. In this embedding, for every vertex $x\in V(G)$, every portion of the curve $f(x)$ between two crossing points has up to $\delta$ edges of $G$ embedded close to it. The embedding of any edge $vw\in E(G)$ crosses at most $\delta$ other curves $f(x_1),\ldots,f(x_d)$ and each of these curves $f(x_i)$ is used to embed at most $\delta$ edges incident to $x_i$.  Therefore the embedding of any edge $vw\in E(G)$ crosses at most $\delta^2$ other edges.  
\end{proof}

>>>>

\begin{lem}
  Every $(g,\delta)$-string graph $G$ is a $(g,2\delta^2)$-planar graph.
\end{lem}

\begin{proof}
  Consider some $(S,\delta)$-string representation, $f$, of $G$.  We will describe an embedding of $G$ into $S$ that is an $(S,k)$-plane graph.  Each vertex $v\in v(G)$ is embedded at $f(v)(0)$. For each edge $vw\in E(G)$ there is an intersection point $p$ between $f(v)$ and $f(w)$, i.e., $f(v)(t_0)=f(w)(t_1)=p$ for some $t_0,t_1\in[0,1]$.  Embed the edge $vw$ very close to the curve whose image is $\{f(v)(t): 0\le t\le t_1\}\cup f(w)(t): 0 \le t\le t_2\}$. The embedding of any edge $vw\in E(G)$ is contained in $f(v)$ and $f(w)$.  Therefore the embedding of $vw$ crosses at most $2\delta$ other curves $f(x_1),\ldots,f(x_d)$.  Each curve $f(x_i)$ is used to embed at most $\delta$ edges incident to $x_i$.  Therefore the embedding of any edge $vw\in E(G)$ crosses at most $2\delta^2$ other edges.  
\end{proof}
